Very simplified likelihood

### 2024-10-11 inst/very_simplified_likelihood.Rmd
off-by-one error fixing

Now some likelihood visuals.  Suppose $r=4,n=8$:

```{r,label=likevis,cache=F}
plotter <- function(...){
a <- seq(from=0,to=1,by=0.01)
n <- 9 # the FC and 8 clones
jj <- exp(f_vec_arn(a,3,n))
plot(a,jj/max(jj,na.rm=TRUE),type='n',xlab=expression(a),ylab="likelihood")
grid()
rain <- rainbow(n)
for(r in seq_len(n)){
  y <- exp(f_vec_a(a,r,n))
  if(r==1){y[length(y)] <- 1}
  y <- y/max(y,na.rm=TRUE)
  if(r>1){y[length(y)] <- 0}
  points(a,y,type='l',lwd=4,col=rain[r])
}
abline(v=MLE(r=5,n=8))
text(0.09,0.95,"r=9",col=rain[9])
text(0.18,0.93,"r=8",col=rain[8])
text(0.25,0.90,"r=7",col=rain[7])
text(0.29,0.83,"r=6",col=rain[6])
text(0.33,0.76,"r=5",col=rain[5])
text(0.35,0.65,"r=4",col=rain[4])
text(0.39,0.54,"r=3",col=rain[3])
text(0.45,0.41,"r=2",col=rain[2])
text(0.59,0.21,"r=1",col=rain[1])
}

@@

```{r shown4n8mle}
MLE(r=5,n=8)
```

>>>>

Now some likelihood visuals.  Suppose $n=9$:

```{r,label=likevis,cache=F}
plotter <- function(...){
a <- seq(from=0,to=1,by=0.01)
n <- 9 # the FC and 8 clones
jj <- exp(f_vec_arn(a,3,n))
plot(a,jj/max(jj,na.rm=TRUE),type='n',xlab=expression(a),ylab="likelihood")
grid()
rain <- rainbow(n)
for(r in seq_len(n)){
  y <- exp(f_vec_a(a,r,n))
  if(r==1){y[length(y)] <- 1}
  y <- y/max(y,na.rm=TRUE)
  if(r>1){y[length(y)] <- 0}
  points(a,y,type='l',lwd=4,col=rain[r])
}
abline(v=MLE(r=5,n=9))
text(0.09,0.95,"r=9",col=rain[9])
text(0.18,0.93,"r=8",col=rain[8])
text(0.25,0.90,"r=7",col=rain[7])
text(0.29,0.83,"r=6",col=rain[6])
text(0.33,0.76,"r=5",col=rain[5])
text(0.35,0.65,"r=4",col=rain[4])
text(0.39,0.54,"r=3",col=rain[3])
text(0.45,0.41,"r=2",col=rain[2])
text(0.59,0.21,"r=1",col=rain[1])
}

@@

```{r shown4n8mle}
MLE(r=5,n=9)
```
